Geometric variational problems

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
fixed one last typo

The proposed mathematical analysis, modeling, and numerical algorithms
will transform our understanding of the collective dynamics of
amphiphilic particles such as (1) their self-assembly into micelles and
bilayers, (2) the material properties of such self-assembly, and (3) the
interaction between these building blocks. In addition to biophysical
applications, amphiphilic Janus particles have recent popularity in the
fabrication of smart materials. The proposed work will have a
transformative impact on precision design for specific mechanical
properties of materials made of amphiphilic nanoparticles. An important
component of this proposal is the interdisciplinary education and
training of both undergraduate students, graduate students, and
postdoctoral fellows. The combination of mathematical modeling,
analysis, and scientific computing in this project provides a compelling
example of the importance of mathematics and computation in biophysics
and engineering applications. The concepts and methods described here go
beyond the context of amphiphilic particles and lipid molecules. They
extend to other problems featuring microscopic phase separation that
leads to formation of mesoscopic domains. This situation arises, for
example, in biological development in systems biology. The methods
developed here have the potential to impact those and other related
areas in biomedicine and biotechnology.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
The topics of this proposal have application in robotics, machine
learning, and engineering. To foster training in mathematical sciences,
the project will include undergraduate researchers (URs). The proposal
supports one UR per year from the lead institution, and will include one
or two additional UR from actively supported in-house programs

>>>>

This project aims to advance the mathematical modeling of collective 
dynamics of amphiphilic particles. The simulations use a new, yet intuitive,
approach that can reach important and complex systems that are presently out of 
reach in computational material science. These complex systems include 
fusion and fission of amphiphilic bilayer membranes and optimal shape design
in metamaterials. The development of three-dimensional 
models describing colloidal systems could be transformative in biomedicine
and material science. The research draws from expertise in scientific 
computing, physics of fluids and mathematics. The mathematical component 
incorporates leading techniques from geometric analysis and gives deep insight 
into fundamental material science. The project offers undergraduates 
in a socially impactful manner the opportunity to do research and train 
with graduate and postdoctoral personnel. It incorporates research in the 
classroom, and with its combination of mathematical modeling, analysis, 
and scientific computing, the project highlights the importance of 
mathematics and computation to all areas of science and engineering.

%The proposed mathematical analysis, modeling, and numerical algorithms
%will transform our understanding of the collective dynamics of
%amphiphilic particles such as (1) their self-assembly into micelles and
%bilayers, (2) the material properties of such self-assembly, and (3) the
%interaction between these building blocks. In addition to biophysical
%applications, amphiphilic Janus particles have recent popularity in the
%fabrication of smart materials. The proposed work will have a
%transformative impact on precision design for specific mechanical
%properties of materials made of amphiphilic nanoparticles. An important
%component of this proposal is the interdisciplinary education and
%training of both undergraduate students, graduate students, and
%postdoctoral fellows. The combination of mathematical modeling,
%analysis, and scientific computing in this project provides a compelling
%example of the importance of mathematics and computation in biophysics
%and engineering applications. The concepts and methods described here go
%beyond the context of amphiphilic particles and lipid molecules. They
%extend to other problems featuring microscopic phase separation that
%leads to formation of mesoscopic domains. This situation arises, for
%example, in biological development in systems biology. The methods
%developed here have the potential to impact those and other related
%areas in biomedicine and biotechnology.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
The topics of this proposal have application in robotics, machine
learning, and engineering. To foster training in mathematical sciences,
the project will include undergraduate researchers (URs). The proposal
supports one UR per year from the lead institution, and will include one
or two additional URs from actively supported in-house programs
